% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\textheight = 10in
\begin{document}

\name{Robert Perry Hooker}
% \address used twice to have two lines of address
\address{\texttt{perry@rphv.net} | 317.695.9860  }
\address{116 Strand Avenue, Missoula, MT 59801}

 
\begin{resume}
 
%\section{\sc Objective}  An intership to gain experience working with high technology.
 
\section{\sc Education} 
        {\sl Master of Science:} Computer Science\\
        University of Montana: Missoula, MT, May 2012\\
        \\
        {\sl Bachelor of Science:} Geology, Mathematics \\
        Western State College: Gunnison, CO, May 2005 \\
        Concentration: Petroleum Geology
 
\section{\sc Computer \\ Skills} {\sl Languages:} Python, C, C\verb!++!, Perl, \LaTeX, et. al.\\
        Experienced with RHEL, Ubuntu, Mac OSX, and Windows operating systems; git, mercurial, make, bash  \\
        \texttt{http://careers.stackoverflow.com/rphv}

\section{\sc Professional Experience} 
        {\sl Software Developer} \hfill  Fall 2012 - Fall 2013\\
        TerraEchos, Inc. \hfill {\sl Missoula, MT}
        \begin{itemize} \itemsep -2pt
            \item using IBM\textsuperscript{\textregistered} InfoSphere Streams.
            \item Implemented distributed machine learning algorithms 
            \item Developed video analytics application using 
            \item Constructed unit-test framework for a Streams-based NIDS.
            \item Programmed Streams operators for object detection, face recognition, and speech recognition.  
        \end{itemize}

        {\sl Computer Scientist} \hfill  Summer 2012\\
        US Forest Service Fire, Fuel, and Smoke Science Program \hfill {\sl Missoula, MT}
        \begin{itemize} \itemsep -2pt
            \item Synthesized multispectral satellite imagery and CFD fire models to assess the impact of mountain pine beetles on forest fires.
        \end{itemize}

        {\sl Teaching Assistant} \hfill  Fall 2011 - Spring 2012\\
        University of Montana Department of Computer Science \hfill {\sl Missoula, MT}
        \begin{itemize} \itemsep -2pt
            \item Responsible for one section of CSCI 172: Intro to Computer Modeling.
            \item Delivered weekly lectures and taught lab sections.
        \end{itemize}

        {\sl Intern, Global Network Operations Center} \hfill  Summer 2011\\
        Indiana University \hfill {\sl Bloomington, IN}
        \begin{itemize} \itemsep -2pt
            \item Worked with the Research Technologies group to upgrade their High Performance Storage System (HPSS).
            \item Translated \verb!noweb! source code for IU's High Performance Storage System.
        \end{itemize}

        {\sl Programmer} \hfill Spring - Summer 2010\\
        Orbital Software \hfill {\sl Missoula, MT}
        \begin{itemize} \itemsep -2pt
            \item Implemented SMS interface for a web-based employee scheduling system.
            \item Produced, edited, and distributed training \& support videos.
        \end{itemize}

%       {\sl IT Support Desk} \hfill Fall 2009\\
%       University of Montana School of Business Administration \hfill {\sl Missoula, MT}
%       \begin{itemize} \itemsep -2pt
%           \item Responsible for software and hardware deployment and support in the SoBA.
%       \end{itemize}

        {\sl Geologist} \hfill 2005 - 2009 \\
        Miranda Gold Corp. \hfill {\sl Elko, NV}
        \begin{itemize}  \itemsep -2pt % reduce space between items
            \item Provided company-wide GIS support.
            %\item Generated and managed proprietary geodatabases for minerals exploration.
            \item Performed statistical analyses of geochemical data for minerals exploration.
            \item Supervised field exploration, data collection, and surveying tasks.
        \end{itemize}

        %{\sl Correspondent} \hfill 2007 - 2009 \\
        %Elko Daily Free Press \hfill {\sl Elko, NV}
        %\begin{itemize}  \itemsep -2pt % reduce space between items
        %   \item Wrote \& photographed a series of articles on local outdoor recreation.
        %\end{itemize}
    
\section{\sc Academic\\ Work}

        Functional Encryption as Mediated Obfuscation (Thesis) \hfill Spring 2012\\
            \emph{MO is a new theoretical model for software protection using functional encryption. \\
            Winner: Outstanding Graduate Student Presentation, 2012 UMT GradFac Conference}\\
%       Predicting Feedback Shift Registers\hfill Spring 2011\\
%           \emph{Machine learning algorithms can predict non-linear feedback shift registers.} \\   
%       RNA Secondary Structure Prediction \hfill Fall 2010\\
%           \emph{The structure \& function of an RNA molecule can be derived from its nucleotides.}\\
%       Algebraic Multigrid can Precondition Krylov Methods \hfill Spring 2010\\
%           \emph{A large linear system can be solved quickly with a hierarchy of smaller systems.} \\
%       uFind Kiosk \hfill Spring 2010\\
%           \emph{A self-help kiosk system for the UMT bookstore incorporates voice recognition.}

References available on request.
\end{resume}
\end{document}
